Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-03-30 draft.tex
change the first paragraph in section 3

It is difficult to experiment with concurrently running jobs on HPC system~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}. One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will. Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results. The third reason is that configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being. Therefore, we resort to simulation in our work.

@@

We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent of a wide array of applications running on leadership-class supercomputers. Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).

@@

\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000 \cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory. It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.

@@

The parameters for building the dragonfly network studied in our work are inspired by the model proposed by Kim et. al~\cite{kim-micro}. Our dragonfly network consists of 33 groups, each of which contains 8 routers. Each router has four compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}. In this work, we study both the network performance and job interference when six different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table~\ref{tab: placement routing configs}.

@@

    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router. We analyze the traffic on the terminal link, local and global channel of each router.

    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of a certain port in the router is full. We analyze the saturated time of ports corresponding to terminal link, local and global channel.

    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks. \footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in our experiments.
}

@@

\section{Study of Parallel Workload~\Rmnum{1}}
%\section{Identify the ``Bully"}
\label{sec:workload-1}

We study the network performance and job interference from two perspectives. Firstly, we analyze the network performance when Workload \Rmnum{1} is running under different placement and routing configurations. Secondly, we isolate each job from the workload, and analyze the interference by scrutinizing the traffic going through the routers that serve each job. The analysis allows us to identify the ``bully" in the workload.

>>>>

Configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being. Even with access to systems with such networks, job placement and routing policies are part of system configuration, which is impossible for user to make changes at will~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}. Therefore, we resort to simulation in our work.

%It is difficult to experiment with concurrently running jobs on HPC systems~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}. One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will. Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results. The third reason is that configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being. Therefore, we resort to simulation in our work.

@@

We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent a wide array of applications running on leadership-class supercomputers. Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).

@@

\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000~\cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory. It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.

@@

The parameters for building the dragonfly network studied in our work are inspired by the model proposed by Kim et. al~\cite{kim-micro}. Our dragonfly network consists of 33 groups, each of which contains eight routers. Each router has four compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}. In this work, we study both the network performance and job interference when six different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table~\ref{tab: placement routing configs}.

@@

    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router. We analyze the traffic on the terminal link, local and global channel of each router. The network reaches optimal performance when the traffic is uniformly distributed and no particular router is over-loaded.

    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of a certain port in the router is full. We analyze the saturated time of ports corresponding to terminal link, local and global channel. The saturated time indicates the congestion level of routers.

    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks. The performance of each application is measured by the communication time.  
\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in the experiments.
}

@@

\section{Study of Parallel Workload~\Rmnum{1}}
%\section{Identify the ``Bully"}
\label{sec:workload-1}
The study of parallel workload~\Rmnum{1} consists of two parts. Firstly, we analyze the over-all network performance when Workload \Rmnum{1} is running under different placement and routing configurations. Secondly, we isolate each application from the workload, analyzing its performance and the interference form its peers by scrutinizing the traffic going through the routers that serve each job. The analysis allows us to identify the ``bully" in the workload.
